This is a qmd for miscellaneous calculations and transformations that needs to happen with the data for SNP-GLM-AED that I really ought to keep track of. 


Fill time series gaps. If there were gaps in time series, I could use tsibble to fill them. Somehow, neither of my time series has gaps, despite them saying they do and spotting gaps last time I looked at them. 
```{r fill time series gaps}
test1 <- read_csv('./sim/inputs/oneInflow_14Jun19_2.csv') |>  
tsibble::as_tsibble(index  = time) |> #\
tsibble::has_gaps()

inflow <- read_csv('./sim/inputs/oneInflow_14Jun19_2.csv') |>  
tsibble::as_tsibble(index  = time) |> #\
tsibble::fill_gaps()|>
mutate(across(FLOW:SALT, ~zoo::na.approx(.x, maxgap  = 5)))

summary(inflow)
```
```{r met data}
met <- read_csv('./sim/inputs/SunapeeMet_1979_2020EST.csv')

met %>% filter(time > "2016-03-28 23:23:59" & time < "2016-03-30 00:00:00")
```

```{r outflow}

outflow <- read_csv('./sim/inputs/corr_outflow_impmodel_baseflow_23Mar2017.csv')|>  
tsibble::as_tsibble(index = time) |> #\
tsibble::count_gaps()

outflow %>% filter(time > "2016-03-01" & time < "2017-04-30")

tail(outflow)

```




Read in and look at Sugar River discharge data and Sunapee Lake level data
*there are some gaps. Currently interpolating with approx, max gap = 1 day. 
*The maximum discharge in the time series from 2016-05-17 - 2025-03-24 is 24.3525m3ps
*plotting a time series to make sure that it looks reasonable
*the 3 points above 24m3ps look unreasonably high and discharge around them does not match. I am excluding them from the original data, then interpolating over those times.

```{r Sugar River Outflow}

snp_discharge <- read_csv("./real_data/SugarRiverDischarge.csv")
snp_discharge_mps<- snp_discharge %>% rename(discharge_cfs = "Observed River Discharge (CFS)") %>% 
  mutate(discharge_m3ps = (discharge_cfs*0.028316847)) %>% 
  #filter(discharge_m3ps < 24) #excluding discharge greater than 24m3ps
summary(snp_discharge_mps)
snp_discharge_mps %>% tsibble::as_tsibble(index  = Datetime) |> #\
tsibble::has_gaps() 

snp_discharge_mps %>%  #check for gaps!
  tsibble::as_tsibble(index  = Datetime) |> 
  tsibble::count_gaps() 

snp_discharge_gapfree <- snp_discharge_mps %>%  #fill gaps using na.approx
  tsibble::as_tsibble(index  = Datetime) |>
  tsibble::fill_gaps()|>
mutate(across(discharge_cfs:discharge_m3ps, ~zoo::na.approx(.x, maxgap  = 1))) #%>% #this approximates gaps as large as one day. Probably don't want to go larger than that here, since this is hourly discharge
 # tsibble::count_gaps()

snp_discharge_mps %>% ggplot(aes(x = Datetime, y = discharge_m3ps)) + geom_point()

```

Sunapee Lake Level
*Data extent: 2010-04-21 to 2025-03-24
*full pool is 1093.15ft, 333.1921m
*datetime is in EDT!!!
```{r}
snp_llevel <- read_csv("./real_data/SNP_level_2010-Mar2025.csv")

snp_level<- snp_llevel %>% rename(level_ft = "Observed Reservoir Pool Elevation (FT)") %>% 
  rename(datetime = "Datetime (EDT)") %>% 
  filter(datetime != "2018-12-28 20:00:00" & datetime != "2018-12-28 19:00:00" & datetime != "2018-12-28 18:00:00" & datetime != "2018-12-28 16:00:00" & datetime != "2018-12-28 17:00:00") %>%  #exclude weird level data %>% 
  mutate(level_m = (level_ft*0.3048)) 

summary(snp_level)
snp_level %>% tsibble::as_tsibble(index  = datetime) |> #\
tsibble::has_gaps() 

snp_level %>%  #check for gaps!
  tsibble::as_tsibble(index  = datetime) |> 
  tsibble::count_gaps() 

snp_level_gapfree <- snp_level %>%  #fill gaps using na.approx
  tsibble::as_tsibble(index  = datetime) |>
  tsibble::fill_gaps()|>
mutate(across(level_ft:level_m, ~zoo::na.approx(.x, maxgap  = 1))) #this seems to be interpolating across more than 1 days worth of gaps. Why, How?

snp_level_gapfree %>% ggplot(aes(x = datetime, y = level_m)) + geom_point()
snp_level %>% 
  #filter(datetime < "2023-12-01 00:00:00" & datetime > "2015-01-01 00:00:00") %>% 
  ggplot(aes(x = datetime, y = level_m)) + geom_point()
```

```{r get the met data}
site = "sunp"
noaa_met <- arrow::open_dataset(arrow::s3_bucket(paste0("bio230121-bucket01/flare/drivers/met/gefs-v12/stage3/site_id=", site),
                                   endpoint_override = "https://amnh1.osn.mghpcc.org",
                                   anonymous = TRUE)) |>
  #filter(variable %in% c("air_temperature", "precipitation_flux")) |> 
  collect() |> 
  reframe(.by = all_of(c("datetime", "variable")), mean_prediction = mean(prediction)) |> 
  pivot_wider(names_from = 'variable', values_from = 'mean_prediction') |> 
  rename(AirTemp = air_temperature) |> 
  mutate(AirTemp = AirTemp - 273.15)

noaa_met_2 <- noaa_met |> 
  mutate(WindSpeed = sqrt(eastward_wind^2 + northward_wind^2)) |> 
  #group_by(date(datetime)) |> 
  mutate(ShortWave = (surface_downwelling_shortwave_flux_in_air), LongWave = (surface_downwelling_longwave_flux_in_air), AirTemp = (AirTemp), RelHum = (relative_humidity * 100), WindSpeed = (WindSpeed), Rain = sum(precipitation_flux)) |> 
  mutate(time = datetime) |> 
  mutate(RelHum = ifelse(RelHum > 100, 100, RelHum)) %>% 
 # ungroup() |>
  select(time, ShortWave, LongWave, AirTemp, RelHum, WindSpeed, Rain) |> 
  distinct()

write.csv(x = noaa_met_2,file = paste0("SunapeeMet_Stage3_", Sys.Date(), ".csv"), row.names = FALSE, quote = FALSE)
```

```{r get met data based on FLARE code}

```



```{r outflow}
#using the inflow as the outflow for now
#this comes from InflowPrep.qmd, but being lazy

outflow <- Inflow_file |> 
  select(time, FLOW)

write.csv(x = outflow,file = paste0("OutflowequalsInflow_", Sys.Date(), ".csv"), row.names = FALSE, quote = FALSE)

outflow <- read_csv("~/SUNP-GLM_AED/InflowsSGR/SugarOutflow.csv")

outflow %>%
  mutate(discharge_m3s = discharge_cfs * 0.028316847) %>% 
  ggplot(aes(x = date, y = discharge_m3s)) + geom_point()

```

need to pull from git ideally

```{r get buoy data}


# headers = read.csv("~/GitHubRepos/CareyLabVT/SUNP-phytocasts/Data/SUNP_buoy_wq.csv", skip = 1, header = F, nrows = 1, as.is = T)
# df = read.csv("~/GitHubRepos/CareyLabVT/SUNP-phytocasts/Data/SUNP_buoy_wq.csv", skip = 4, header = F)
# colnames(df)= headers
# # headers = read.csv("~/GitHubRepos/CareyLabVT/SUNP-phytocasts/Data/temp1m.csv", skip = 0, header = F, nrows = 1, as.is = T)
# # df = read.csv("~/GitHubRepos/CareyLabVT/SUNP-phytocasts/Data/temp1m.csv", skip = 1, header = F)
# # colnames(df)= headers
# oldbuoy <- df

```

